    \section{Tesla Motors}

\subsection{A little bit of history}
\begin{frame}
\frametitle{A little bit of history}
\begin{itemize}
    \itemsep1em
    \item Cars were powered by electricity in 1903
        % Invented the electric starter to just keep the noise inconvenience
        % compared to electrical motors
    \item Ford needed to reduce the production costs of cars production
    \item Developing a new way to produce faster % mass production
    \item Seems to have worked since 1908 and the Ford T
    \item Product advertisement was not needed between 1917 and 1923
\end{itemize}
\end{frame}

\subsection{The weird kid in the playground}
\begin{frame}
\frametitle{Everyone sees the potential of an electric car}
\begin{itemize}
    \itemsep1.5em
    \item Smooth feeling on the road
    \item Decrease the dependency to oil
    \item Reduces the pollution released compares to classic cars
    \item Everybody seems to agree it is the future car
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{But…}
\begin{itemize}
    \itemsep1.5em
    \item What about the autonomy?
    \item The drive might be slow… no?
    \item Reducing the pollution… really? % preconceived ideas
    \item It has to be today? Not… like… in 20 years?
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{No one wants electric cars to be on the market}
\begin{itemize}
    \itemsep1.5em
    \item Selling classic cars would be difficult % 10 parts compared to 200
    \item Requires investments
    \item Lobbying by the oil industry  % case with the BBC
    \item Governments are not pushing it enough % because they impose taxes on
        % oil and do not want to afraid "classic" constructors. Plus, the US is
        % a big oil producer
\end{itemize}
\end{frame}


\subsection{The autonomy is a real issue}

\begin{frame}
\frametitle{The autonomy is the real issue}
\begin{itemize}
    \itemsep1.5em
    \item AC Propulsion
    \item Maximum range: 250 miles
    \item No station to charge the car
    \item The most criticized point
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Superchargers}
\begin{itemize}
    \itemsep1.5em
    \item 60 miles of range for every 10 minutes
    \item Battery swap, \$60--\$80
    \item Fast or free
\end{itemize}
\end{frame}


\begin{frame}
\frametitle{Solarcity and batteries manufacture}
\begin{itemize}
    \itemsep1.5em
    \item
\end{itemize}
\end{frame}


\begin{frame}
\frametitle{Hyperloop}
\begin{itemize}
    \itemsep1.5em
    \item Maybe there will be some slots for cars in it ;) ;)
\end{itemize}
\end{frame}


\subsection{A plan in 3 big steps}

\begin{frame}
\frametitle{Electric cars can be cool}
\begin{itemize}
    \itemsep1em
    \item Tesla Roadster Sport
    \item Powerful: 0--60 mph in 3.70 seconds
    \item Range: 244 miles (393km)
    \item US \$128,500
    \item No compromise
    % At this step, Musk has to reinvest a big part of his money or tesla would
    % die
\end{itemize}
\end{frame}

\begin{frame}
\begin{itemize}
    \itemsep1.5em
    \item Efficiency of battery-to-wheel motor: 88\% on average
        % For comparison, internal combustion engines have a tank-to-wheel
        % efficiency of about 15%
        % https://en.wikipedia.org/wiki/Tesla_Roadster#Energy_efficiency
    \item Regular cool free upgrades
    \item 1st automobile constructor in the Silicon Valley
    \item A lot of gadgets
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Electric cars can be classy}
\begin{itemize}
    \itemsep1.5em
    \item Model S and then Model X
    \item More ``affordable'': US\$80,000
    \item Range: 320 miles (520km)
    \item Autopilot and cool features
    \item Really good reviews
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Not only rich peoples can buy a good electric car}
\begin{itemize}
    \itemsep1.5em
    \item Model 3
    \item Scheduled for 2017
    \item Should cost around US\$35,000
    \item Government's \$7500 EV tax credit
\end{itemize}
\end{frame}
