    \section{Inspired by the Ford's strategies}

\subsection{A little bit of history}
\begin{frame}
\frametitle{A little bit of history}
\begin{itemize}
    \itemsep1em
    \item Cars were electrics in 1903
    \item Ford needed to reduce the production costs of thermal engines
    \item Developing a new way to produce faster
    \item Seems to have worked since 1908 and the Ford T
    \item Product advertisement was not needed between 1917 and 1923
\end{itemize}
\end{frame}

\subsection{Electric cars}
\begin{frame}
\frametitle{No one wants electric cars to be on the market}
\begin{itemize}
    \itemsep1.5em
    \item Selling classic cars would be difficult
    \item Requires investments
    \item Lobbying by the oil industry
    \item Governments are not pushing it enough
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Everyone wants an electric car}
\begin{itemize}
    \itemsep1.5em
    \item Smooth feeling on the road
    \item Decrease the dependency to oil
    \item Reduces the pollution released compares to classic cars
    \item Everybody seems to agree it is the future car
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{But…}
\begin{itemize}
    \itemsep1.5em
    \item What about the autonomy?
    \item The drive might be slow… no?
    \item Reducing the pollution… really?
    \item OK but… it has to be today? Not… like… tomorrow?
\end{itemize}
\end{frame}


\subsection{Space travels}

\begin{frame}
\frametitle{Space travels}
\begin{itemize}
    \itemsep1.5em
    \item Technology issues
    \item High costs
\end{itemize}
\end{frame}
